The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-15 paper/ms.tex
beta cep

\begin{figure*}
\plotone{98_Tau_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}. The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse, though this did not adversely affect the pointing systematics model. The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}
\label{fig:98tau}
\end{figure*}

@@

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars with self-driven nonradial modes.

>>>>

\begin{figure*}
\plotone{98_Tau_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}. Blacked-out pixels in the halo weights are background stars which were manually set to zero weight by hand. The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse, though this did not adversely affect the pointing systematics model. The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}
\label{fig:98tau}
\end{figure*}

@@

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry and asteroseismology of the Hyades giants, and main-sequence stars with self-driven nonradial modes.
